---
title: "Alcohol vs Seat choice"
author: "Cynthia Tellez"
date: "Fall 2021"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

Visually, the plot shows a large difference between the back row and middle row. The plot shows a significantly larger difference between the back row and the front row.

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

According to our data table, all rows do not have the same average total of drinks. The back row seems to drink an average amount of 8.6 drinks per week, more than twice what the middle row drinks on a weekly basis (3.3 drinks), and about seven times more than what the front row drinks (1.8 drinks). It is reasonable to assume that each row is not drinking the same amount of drinks per week.

## Inferential Tests

## Conclusions


